---
title: "MEFAdapt energy data"
author: "MEFAdapt project"
date: "2025"
output:
  html_document:
    theme:
      bootswatch: flatly
    toc: true
    toc_depth: 2
params:
    countrydata: NA
cache: FALSE
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


libraries <- c(
    "rmarkdown", "bslib", "Rcpp", "reticulate",
    "aws.s3", "lubridate", "tibble", "kableExtra", "shiny",
    "stringi", "aws.signature", "ggpubr", "stringr", "knitr", "ggsci",
    "ggsflabel", "ggthemes", "janitor", "magrittr", "tidyverse",
    "dplyr", "DT"
)

lapply(libraries, library, character.only = TRUE)

options(knitr.table.format = "html")

options(scipen = 999)

bucket <- "mefadapt"

aws.signature::use_credentials(profile = "mefadapt")

Sys.setenv("AWS_DEFAULT_REGION" = get_location("mefadapt"))
```



```{r read.data, warning=FALSE, include=FALSE}
en.table <- s3read_using(read.csv,
    row.names = 1,
    object = "repository/global_analysis/energy/sp_energy.csv",
    bucket = bucket
) %>%
    select(-PLANT_KEY) %>%
    unique()

# en.gis <- s3read_using(
#     st_read,
#     object = "repository/global_analysis/energy/sp_energy.gpkg",
#     bucket = bucket
# )
```

<br>

# A short walktrough the data


The S&P energy data contains information on `r nrow(en.table)` energy plants globally.
It contains information on their location, the type of technology used for production, operating status, and others.


<br>
<br>


## Energy type


This is the list of commodities that are explored in the dataset.
'n' is the number of mines that explore each commodity, and 'perc' is the percentage of plants with each technology.


<br>
<br>


```{r}
en.table %>%
    count(TECH_TYPE) %>%
    mutate(sum = sum(n)) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown"))) %>%
    mutate(perc = round(n * 100 / sum, 1)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(class = "cell-border stripe"))
```

<br>

The table below shows the relationship between the technology type and fuel type in the same power plant.


<br>
<br>


```{r}
en.table %>%
    count(TECH_TYPE, FUEL_TYPE) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```


<br>
<br>


## Operational status


The table below shows the operational status of these power plants, according to the dataset.


<br>
<br>


```{r}
en.table %>%
    count(OPER_STATUS) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```


<br>
<br>

## Operational and planned capacity

The table below is a short summary of data availability regarding planned and operating capacity, for each operating status.

The first column shows the number of plants with available data on operational capacity, and the second column shows the number of plants with available data on planned capacity.
The last column shows the number of plants in the database for each operational status.

<br>
<br>

```{r}
en.table %>%
    mutate(
        OPER_CAPACITY_PLANT = ifelse(is.na(OPER_CAPACITY_PLANT), 0, 1),
        PLANNED_CAPACITY = ifelse(is.na(PLANNED_CAPACITY), 0, 1)
    ) %>%
    group_by(OPER_STATUS) %>%
    summarize(
        OPER_CAPACITY_PLANT = sum(OPER_CAPACITY_PLANT, na.rm = T),
        PLANNED_CAPACITY = sum(PLANNED_CAPACITY, na.rm = T),
        n = n()
    ) %>%
    ungroup() %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
Below is a summary of the operating and planned capacity, per fuel type.


<br>
<br>


```{r}
en.table %>%
    group_by(FUEL_TYPE) %>%
    summarize(
        OPER_CAPACITY_PLANT = round(sum(OPER_CAPACITY_PLANT, na.rm = T), 0),
        PLANNED_CAPACITY = round(sum(PLANNED_CAPACITY, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    select(-PLANNED_CAPACITY) %>%
    arrange(desc(OPER_CAPACITY_PLANT)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

en.table %>%
    group_by(FUEL_TYPE) %>%
    summarize(
        OPER_CAPACITY_PLANT = round(sum(OPER_CAPACITY_PLANT, na.rm = T), 0),
        PLANNED_CAPACITY = round(sum(PLANNED_CAPACITY, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    select(-OPER_CAPACITY_PLANT) %>%
    arrange(desc(PLANNED_CAPACITY)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

Finally, below is a summary of the operating and planned capacity, per fuel and technology type.


<br>
<br>


```{r echo=FALSE}
en.table %>%
    group_by(TECH_TYPE, FUEL_TYPE) %>%
    summarize(
        OPER_CAPACITY_PLANT = round(sum(OPER_CAPACITY_PLANT, na.rm = T), 0),
        PLANNED_CAPACITY = round(sum(PLANNED_CAPACITY, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    select(-PLANNED_CAPACITY) %>%
    arrange(desc(OPER_CAPACITY_PLANT)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```


<br>
<br>


```{r echo=FALSE}
en.table %>%
    group_by(TECH_TYPE, FUEL_TYPE) %>%
    summarize(
        OPER_CAPACITY_PLANT = round(sum(OPER_CAPACITY_PLANT, na.rm = T), 0),
        PLANNED_CAPACITY = round(sum(PLANNED_CAPACITY, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    select(-OPER_CAPACITY_PLANT) %>%
    arrange(desc(PLANNED_CAPACITY)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```



<br>
<br>


Below are other summaries of the operational and planned capacity, per fuel type.
The first table shows the total operational capacity, planned capacity, number of plants, minimum, maximum and mean operational capacity, and minimum, maximum and mean planned capacity.


<br>
<br>

```{r echo=FALSE}
en.table %>%
    filter(OPER_CAPACITY_PLANT > 0) %>%
    group_by(FUEL_TYPE) %>%
    summarize(
        total_operating_capacity = round(sum(OPER_CAPACITY_PLANT, na.rm = T), 0),
        number_of_plants = n(),
        minimum_operating_capacity = round(min(OPER_CAPACITY_PLANT, na.rm = T), 2),
        maximum_operating_capacity = round(max(OPER_CAPACITY_PLANT, na.rm = T), 0),
        mean_operating_capacity = round(mean(OPER_CAPACITY_PLANT, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    arrange(desc(total_operating_capacity)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))



en.table %>%
    filter(PLANNED_CAPACITY > 0) %>%
    group_by(FUEL_TYPE) %>%
    summarize(
        total_planned_capacity = round(sum(PLANNED_CAPACITY, na.rm = T), 0),
        number_of_plants = n(),
        minimum_planned_capacity = round(min(PLANNED_CAPACITY, na.rm = T), 2),
        maximum_planned_capacity = round(max(PLANNED_CAPACITY, na.rm = T), 0),
        mean_planned_capacity = round(mean(PLANNED_CAPACITY, na.rm = T), 0)
    ) %>%
    ungroup() %>%
    arrange(desc(total_planned_capacity)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

Below are all the planned and existing plants with capacity higher than 14000.


<br>
<br>

```{r echo=FALSE}
en.table %>%
    filter(PLANNED_CAPACITY > 10000) %>%
    rbind(., en.table %>% filter(OPER_CAPACITY_PLANT > 10000)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```



<br>
<br>

The histograms below show the same type of data, but show the full spectrum of operational capacity, and planned capacity, for each fuel type.
The first histogram shows the operational capacity, and the second one shows the planned capacity.

#### Please beware that the y and x axes are not the same for all graphs.
#### This means that the graphs are not directly comparable.

<br>
<br>



```{r cumulative_graphs2, echo=FALSE,fig.height=15, fig.width=10}
t <- en.table %>%
    select(FUEL_TYPE, OPER_CAPACITY_PLANT, PLANNED_CAPACITY) %>%
    pivot_longer(cols = c(OPER_CAPACITY_PLANT, PLANNED_CAPACITY), names_to = "type", values_to = "value") %>%
    mutate(type = ifelse(type == "OPER_CAPACITY_PLANT", "Operational Capacity", "Planned Capacity")) %>%
    filter(value < 10000)

t %>%
    filter(value > 0) %>%
    ggplot(aes(x = value)) +
    geom_histogram(bins = 20, fill = "blue", color = "black", alpha = 0.7) +
    facet_grid(FUEL_TYPE ~ type, scales = "free_y") +
    labs(
        title = "Histograms of Capacity by Fuel Type",
        x = "Capacity",
        y = "Count"
    ) +
    theme_minimal()
```
