---
title: "MEFAdapt mining data"
author: "MEFAdapt project"
date: "2024"
output:
  html_document:
    theme:
      bootswatch: flatly
    toc: true
    toc_depth: 2
params:
    countrydata: NA
cache: FALSE
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


libraries <- c(
    "rmarkdown", "bslib", "Rcpp", "reticulate",
    "aws.s3", "lubridate", "tibble", "kableExtra", "shiny",
    "stringi", "aws.signature", "ggpubr", "stringr", "knitr", "ggsci",
    "ggsflabel", "ggthemes", "janitor", "magrittr", "tidyverse",
    "dplyr", "DT", "tidyverse"
)

lapply(libraries, library, character.only = TRUE)

options(knitr.table.format = "html")

options(scipen = 999)

bucket <- "mefadapt"

aws.signature::use_credentials(profile = "mefadapt")

Sys.setenv("AWS_DEFAULT_REGION" = get_location("mefadapt"))
```



```{r read.data, warning=FALSE, include=FALSE}
mi.table <- s3read_using(read.csv,
    row.names = 1,
    object = "repository/global_analysis/mining/sp_mining.csv",
    bucket = bucket
)


# Function to split and expand each row
expand_row <- function(new_class, actv_status, dev_stage) {
    actv_status_vec <- str_split(actv_status, ",\\s*")[[1]]
    dev_stage_vec <- str_split(dev_stage, ",\\s*")[[1]]
    crossing(
        new_class = new_class,
        actv_status = actv_status_vec,
        dev_stage = dev_stage_vec
    )
}
expand_row2 <- function(new_class, MINING_METHODS) {
    MINING_METHODS_vec <- str_split(MINING_METHODS, ",\\s*")[[1]]
    crossing(
        new_class = new_class,
        MINING_METHODS = MINING_METHODS_vec,
    )
}
classes <- read_delim("C:/Users/RafaelaFlach/Downloads/tempdir/expanded.csv", delim = ";") %>%
    mutate(new_class = ifelse(new_class == "Unknown", "Unknown/Other", new_class))

expanded_cl <- pmap_dfr(classes, expand_row)
cl.list <- unique(classes$new_class)

write.csv(expanded_cl, "C:/Users/RafaelaFlach/Downloads/tempdir/class_expanded.csv")


classes.proc <- read_delim("C:/Users/RafaelaFlach/Downloads/tempdir/new_class_method.csv", delim = ";")

expanded_cl_pr <- pmap_dfr(classes.proc, expand_row2)

write.csv(expanded_cl_pr, "C:/Users/RafaelaFlach/Downloads/tempdir/class_expanded_pr.csv")
# mi.gis <- s3read_using(
#     st_read,
#     object = "repository/global_analysis/mining/sp_mining.gpkg",
#     bucket = bucket
# )

mi.methods <- unique(mi.table$MINING_METHODS) %>%
    as.vector() %>%
    str_split(., ",\\s*") %>%
    unlist() %>%
    unique() %>%
    sort() %>%
    data.frame(methods_original = .)

outtab <- full_join(mi.methods, expanded_cl_pr, by = c("methods_original" = "MINING_METHODS"), keep = TRUE) %>% arrange(methods_original)
write.csv(outtab, "C:/Users/RafaelaFlach/Downloads/tempdir/methods_expanded.csv")
```

<br>
<br>

# A short walktrough the data


The S&P mining data contains information on `r nrow(mi.table)` mines globally.
It contains information on location of these mines, the type of mineral that is explored, and the type of technology used for mining and processing.
However, not all mines have complete information on all variables.

<br>
<br>

## Commodities


This is the list of commodities that are explored in the dataset.
'n' is the number of mines that explore each commodity, and 'perc' is the percentage of mines that explore each commodity.
It is possible to see here that around 35 and 13% of the mines explore gold and copper, respectively.

<br>
<br>

```{r}
mi.table %>%
    count(PRIMARY_COMMODITY) %>%
    mutate(sum = sum(n)) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(perc = round(n * 100 / sum, 1)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(class = "cell-border stripe"))
```

<br>

However, some mines have more than one commodity. The table below shows the relationship between the 'primary commodity' and the other commodities explored in the same mine.
The table is sorted by the number of mines that explore each combination of commodities.

<br>
<br>

```{r}
mi.table %>%
    count(PRIMARY_COMMODITY, COMMODITIES_LIST) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

## Production Methods


The table below shows types of technology used in mining according to the dataset.
As seen here, unfortunately for more than 80% of the mines, this information is not available.

<br>
<br>

```{r}
mi.table %>%
    count(MINING_METHODS) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```


<br>

The same is true for the data on processing methods, and production forms.

<br>
<br>

```{r}
mi.table %>%
    count(PROCESSING_METHODS, PRODUCTION_FORMS) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

## Operation Status


More than 54% of the mines in 
the dataset are inactive, for one reason or another.

<br>
<br>


```{r}
mi.table %>%
    count(ACTV_STATUS) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

These are the types of 'development stages' included in the dataset.

<br>
<br>

```{r}
mi.table %>%
    count(DEV_STAGE) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br>
<br>

And finally, this is the full table with the combinations between 'development stage' and 'operation status'.

<br>
<br>

```{r}
mi.table %>%
    count(DEV_STAGE, ACTV_STATUS) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    mutate(sum = sum(n)) %>%
    mutate(perc = round(n * 100 / sum, 3)) %>%
    select(-sum) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```

<br> 
<br>

# A focus on energy transition minerals


This part of the analysis of the dataset focuses on minerals that are
 important for the energy transition.

These minerals are: Lithium, Cobalt, Nickel, Graphite, 
Rare Earth Elements, Copper, and Manganese.

First, we filter the dataset to include mines that explore 
these minerals more broadly, and then filter to show the mines in which 
these minerals are the primary commodity.

<br>
<br>

```{r}
minerals <- c(
    "Lithium", "Cobalt", "Nickel", "Graphite",
    "Copper", "Manganese"
)

newtable1 <- mi.table %>%
    filter(grepl(paste(minerals, collapse = "|"), COMMODITIES_LIST))


newtable2 <- mi.table %>%
    filter(PRIMARY_COMMODITY %in% minerals)
```


There are `r nrow(mi.table)` mines in the dataset.
Of these, `r nrow(newtable1)` explore at least one of the energy transition minerals,
and `r nrow(newtable2)` have one of these minerals as the primary commodity.	

The table below show how many mines explore these minerals as their primary commodity.

<br>
<br>

```{r}
newtable2 %>%
    count(PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(class = "cell-border stripe"))
```

<br>
<br>


The table below show the number of mines 
in which these minerals are obtained as both a primary or non-primary commodity.

<br>
<br>


```{r}
newtable1 %>%
    count(PRIMARY_COMMODITY) %>%
    mutate(sum = sum(n)) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(class = "cell-border stripe"))
```


<br>
<br>

## Operation Status of Energy Transition Mines

Here we only considered the mines in which the energy transition minerals
are explored as the primary commodity.

<br>
<br>

### Activity status and development stage for each energy transition mineral


<br>
<br>

```{r}
newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[1]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[2]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[3]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[4]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[5]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))

newtable2 %>%
    filter(PRIMARY_COMMODITY == minerals[6]) %>%
    count(ACTV_STATUS, DEV_STAGE, PRIMARY_COMMODITY) %>%
    mutate(across(everything(), ~ replace_na(.x, "Unknown/Other"))) %>%
    arrange(desc(n)) %>%
    datatable(options = list(scrollX = TRUE, class = "cell-border stripe"))
```



<br>
<br>


# Simplifying things


Here we applied a new classification to the status of the mines, based on the
`ACTV_STATUS` and `DEV_STAGE` columns.
This is done to simplify our analysis, and to make it easier to visualize the data.
The new classification is as follows:

- **Early Exploration**: Mines that are in the early stages of exploration, including those that are not yet active.
- **Advanced Exploration**: Mines that are in the advanced stages of exploration, but not yet in production.
- **Study & Evaluation**: Mines that are being studied or evaluated for potential production.
- **Development**: Mines that are in the development stage, preparing for production.
- **Production**: Mines that are actively producing minerals.
- **Closure**: Mines that are in the process of closing down.
- **Rehabilitation**: Mines that are being rehabilitated after closure.
- **Unknown/Other**: Mines that do not fit into any of the above categories, or for which the status is unknown.


<br>
<br>


```{r, include=FALSE, warning=FALSE, message=FALSE}
classes <- read_delim("C:/Users/RafaelaFlach/Downloads/tempdir/expanded.csv", delim = ";")

expanded_cl <- classes

first <- mi.table %>%
    mutate(
        ACTV_STATUS = replace_na(ACTV_STATUS, "Unknown/Other"),
        DEV_STAGE = replace_na(DEV_STAGE, "Unknown/Other")
    ) %>%
    left_join(., expanded_cl %>% filter(dev_stage != "Any"),
        by = c("ACTV_STATUS" = "actv_status", "DEV_STAGE" = "dev_stage")
    )

second <- first %>%
    filter(is.na(new_class)) %>%
    select(-new_class) %>%
    left_join(., expanded_cl %>% filter(dev_stage == "Any") %>% select(-dev_stage), by = c("ACTV_STATUS" = "actv_status"))

all <- rbind(first %>% filter(!is.na(new_class)), second)

test <- all %>%
    filter(is.na(new_class)) %>%
    group_by(DEV_STAGE, ACTV_STATUS) %>%
    summarize(n = n()) %>%
    ungroup() %>%
    arrange(desc(n))



newtable <- all %>%
    mutate_at(vars(new_class), ~ replace_na(.x, "Unknown/Other")) %>%
    filter(PRIMARY_COMMODITY %in% minerals)

t <- newtable %>%
    filter(new_class == "Production") %>%
    filter(!is.na(PRODUCTION_FORMS)) %>%
    dim()


summary <- newtable %>%
    group_by(new_class, PRIMARY_COMMODITY) %>%
    summarize(n = n()) %>%
    ungroup() %>%
    group_by(PRIMARY_COMMODITY) %>%
    mutate(sum = sum(n)) %>%
    ungroup() %>%
    mutate(
        new_class = factor(new_class, levels = cl.list, ordered = T),
        perc = 100 * n / sum
    ) %>%
    arrange(desc(n))

com <- unique(summary$PRIMARY_COMMODITY)

summary <- summary %>%
    mutate(PRIMARY_COMMODITY = factor(PRIMARY_COMMODITY, levels = com, ordered = T))

colors <- c(
    "#dbc1ac", "#967259", "#634832",
    "#f9d62e",
    "#ff4e50",
    "#005582", "#0086ad", "#00c2c7",
    "grey75"
)

plottable <- newtable %>%
    mutate(new_class = factor(new_class, levels = cl.list, ordered = T))
```


<br>
<br>

```{r}
ggplot(summary, aes(x = PRIMARY_COMMODITY, y = n, fill = new_class)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_manual(values = colors) +
    labs(x = "Primary commodity", y = "Number of Mines", title = "Mines by New Class and Primary Commodity") +
    theme_minimal()

ggplot(summary, aes(x = PRIMARY_COMMODITY, y = perc, fill = new_class)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = colors) +
    coord_flip() +
    labs(x = "Primary commodity", y = "% of Mines", title = "Mines by New Class and Primary Commodity") +
    theme_minimal()
```


<br>
<br>

## Geographical distribution of mines for different critical minerals


<br>
<br>

```{r, include=FALSE, warning=FALSE, message=FALSE}
library(rnaturalearth)
library(rnaturalearthdata)

# Create world background polygon using natural earth data
world <- ne_countries(scale = "medium", returnclass = "sf")
```

```{r echo = FALSE, warning=FALSE}
# Create the map with points from newtable
# Assign specific colors to each unique value in cl.list

colors <- c(
    "#dbc1ac", "#967259", "#634832",
    "#f9d62e",
    "#ff4e50",
    "#005582", "#0086ad", "#00c2c7",
    "grey75"
)
color_mapping <- setNames(colors[seq_along(cl.list)], cl.list)

ii <- list()
for (i in com) {
    ii[[i]] <- ggplot() +
        geom_sf(data = world, fill = "white", color = "grey25") +
        geom_point(
            data = plottable %>% filter(PRIMARY_COMMODITY == i),
            aes(x = LONGITUDE, y = LATITUDE, color = new_class), size = 1.5, alpha = 0.7
        ) +
        scale_color_manual(values = color_mapping) +
        facet_wrap(~PRIMARY_COMMODITY, ncol = 1) +
        labs(
            title = paste0("Location of ", i, " mines"),
            x = "Longitude", y = "Latitude",
            color = "New Class"
        ) +
        theme_minimal()
}
```

```{r, fig.width=12, fig.height=8, warning=FALSE, message=FALSE}
for (i in com) {
    plot(ii[[i]])
}
```


<br>
<br>

```{r, include=FALSE, warning=FALSE, message=FALSE}
library(sf)

# Ensure both datasets are in the same CRS
newtable_sf <- st_as_sf(
    newtable %>%
        filter(!is.na(LATITUDE)),
    coords = c("LONGITUDE", "LATITUDE"),
    crs = st_crs(world)
)

# Perform spatial join to find which polygon each point belongs to
newtable_sf <- st_join(newtable_sf, world["name"], join = st_within)

# Add the 'name' column from the polygons to the original table
newtable <- newtable %>%
    filter(!is.na(LATITUDE)) %>%
    mutate(polygon_name = newtable_sf$name)



summary <- newtable %>%
    group_by(new_class, PRIMARY_COMMODITY, polygon_name) %>%
    summarize(n = n()) %>%
    ungroup() %>%
    group_by(new_class, PRIMARY_COMMODITY) %>%
    mutate(sum = sum(n)) %>%
    ungroup() %>%
    mutate(
        new_class = factor(new_class, levels = cl.list, ordered = T),
        perc = 100 * n / sum
    ) %>%
    select(-n, -sum) %>%
    pivot_wider(names_from = new_class, values_from = perc)
```


<br>
<br>

# Further data availability

There is a series of columns in the dataset that could be very helpful for more detailed analysis. However, that data is not available for most of the mines.

Below is a table that shows the percentage of non-missing values for each of these columns, for the mines that are classified as 'Production' in the new classification.

The columns are:
- `MINE_TYPE1`: Type of mine
- `PROJ_START_UP_YR`: Year of project start-up
- `START_UP_YR`: Year of mine start-up
- `MILL_CAPACITY_TONNES_PER_YEAR`: Mill capacity in tonnes per year
- `MINING_METHODS`: Mining methods used
- `PROCESSING_METHODS`: Processing methods used


<br>
<br>

```{r warning=FALSE, message=FALSE}	
coltests <- c("MINE_TYPE1", "PROJ_START_UP_YR", "START_UP_YR", "MILL_CAPACITY_TONNES_PER_YEAR", "MINING_METHODS", "PROCESSING_METHODS")

t <- all %>%
    filter(new_class == "Production") %>%
    select(PRIMARY_COMMODITY, new_class, PROP_ID, all_of(coltests))
commodity_counts <- t %>%
    count(PRIMARY_COMMODITY, name = "mines_count")

t %>%
    group_by(PRIMARY_COMMODITY, new_class) %>%
    summarize(across(
        all_of(coltests),
        ~ 100 - round(mean(is.na(.)) * 100, 0),
        .names = "{.col}"
    ), .groups = "drop") %>%
    left_join(commodity_counts, by = "PRIMARY_COMMODITY") %>%
    select(-new_class) %>%
    datatable(options = list(class = "cell-border stripe"))
```


<br>
<br>